When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-09-25 doc/paper/vpd_et_paper.tex
added vpd paper
back to writing

\begin{linenomath*}
  \begin{equation}
\frac{\partial \;  ET}{\partial \; D} = \frac{g_a \; P}{T(\Delta + \gamma)}   \left(\frac{ c_p}{R_{air}} - \frac{\gamma c_s }{\text{LAI }1.6 \; R\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right) \right)
  \end{equation}
\end{linenomath*}
Note that given yearly uWUE from \cite{Zhou_2015}, $g_1$ from \cite{Lin_2015} \citep[as presented in ][]{Franks_2017}, and observations of R, T, P, D$_s$, and wind speed (WS), the only unknown is LAI. With flux tower observations of ET, LAI will then be uniquely determined for each observation through Equation 6:

\begin{linenomath*}
  \begin{equation}
LAI  = - \frac{g_a \gamma c_s \sqrt{D_s} P }{ \left(\text{ ET } ( \Delta + \gamma) - \Delta R - g_a \rho_a c_p D_{s}\right) 1.6 \; R\; T\; \text{ uWUE } (1 + \frac{g_1}{\sqrt{D_s}})}
  \end{equation}
\end{linenomath*}

@@

We use data from FLUXNET2015. Because $g_1$ coefficients \citep{Lin_2015} and uWUE were only both available for five plant functional types (PFTs - see Table 2),  only 56 of the 77 sites were used. Figure 1 presents each site and its plant functional type.

@@

@@

>>>>

\begin{linenomath*}
  \begin{equation}
    \frac{\partial \;  ET}{\partial \; D} = \frac{g_a \; P}{T(\Delta + \gamma)}   \left(\frac{ c_p}{R_{air}} - \frac{\gamma c_s }{\text{LAI }1.6 \; R\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right) \right)
    \label{d_et}
  \end{equation}
\end{linenomath*}
Note that given yearly uWUE from \cite{Zhou_2015}, $g_1$ from \cite{Lin_2015} \citep[as presented in ][]{Franks_2017}, and observations of R, T, P, D$_s$, and wind speed (WS), the only unknown is LAI. With flux tower observations of ET, LAI will then be uniquely determined for each observation through Equation 6:

\begin{linenomath*}
  \begin{equation}
    LAI  = - \frac{g_a \gamma c_s \sqrt{D_s} P }{ \left(\text{ ET } ( \Delta + \gamma) - \Delta R - g_a \rho_a c_p D_{s}\right) 1.6 \; R\; T\; \text{ uWUE } (1 + \frac{g_1}{\sqrt{D_s}})}
    \label{lai}
  \end{equation}
\end{linenomath*}

@@

We use data from FLUXNET2015. Because $g_1$ coefficients \citep{Lin_2015} and uWUE were only both available for five plant functional types (PFTs - see Table 2),  only 56 of the 77 sites were used. Figure \ref{map_fig} presents each site and its plant functional type.

@@

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig01.pdf}
\caption{Plant functional type and location of sites used in analysis.}
\label{map_fig}
 \end{figure}

@@

By construction, the variability in the LAI term (Equation \ref{lai}) contains all model and observational uncertities. LAI also has physical meaning corresponding to ``true'' leaf area, and we expect that it would be approximately $O(1)$. We can have some confidence in our framework, including the assumption of constant uWUE, if calculated LAIs are generally $O(1)$. Figure \ref{lai_fig} presents the histogram of calculated LAIs with outliers (lowest and highest 5\% percent) and unphysical values (LAI $<$ 0.) removed.
